---
title: "Initial Korean covid 19"
author: "your name here"
date: "todays date"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  
```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex)) 
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex))
basicCC + geom_bar (stat="identity", position = "dodge")
```


  





  
## Numerical results
```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```






When observing the inferential results, I found out that the odds of men to die because of COVID in South Korea is 2.3 times greater than the women, which agrees to the past results, as we saw that most of the dead people because of COVID are mostly men. I also noticed that the P-value 1s low (8.8889), and thus this low value suggests that the chances of males and females dying because of COVID 15 not the same, because men have a higher chance of getting COVID and dying way more than women.


## Inferential results 


When plotting the grphical resuls, I observed that the number of people alive are way higher than dead people. 2/3 of the people with covid were men. 1/3 of the people with covid were women.

## Conclusions

In this assignment, I analyzed COVID data from South Korea. The data was a categorical categorical data, so I used the helper file to complete the assignment. I was able to analyze the data  using graphical, numerical, and inferential results. In the graphical results, I was able to do a chart using ggplot and when I got the charts and observed them. I found out that the number of people alive are way higher than the number of people dead. Also, when looking at the percentage chart, I found that in the chart of dead people 2/3 of it were men (about 63%) and 1/3 were women (about 37%). This suggests that the disease mostly killed males more than females, while in the alive chant most of the alive people were women about 57% compared to men (about 43%).


